---
title: "Chapter 4 Part 1: Solutions"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


```{r include=FALSE}
library(knitr)
```

## In Class Example 1: Aircraft Bearings

The inside diameters of bearings used in an aircraft landing gear assembly are known to have a standard deviation of .002. A random sample of 15 bearings has an average inside diameter of 8.2535 cm.  
Test the hypothesis that the mean inside bearing diameter is 8.25cm. Use a two-sided alternative and a = .05.  


```{r}
null_hypothesis = 8.25
sample_mean = 8.2535
standard_dev = 0.002

z = ((sample_mean - null_hypothesis)/(standard_dev/sqrt(15)))

Range_z <- qnorm(c(.025, .975))
if(Range_z[1] < z & z < Range_z[2]){
  print("Accept")
} else{
  print("Reject")
}


```

## In Class Example 2: Aircraft Bearings Confidence intervals

Construct a 95% two sided confidence interval on the mean bearing diameter using data from the previous question.

```{r}
sample_mean = 8.2535
error = qnorm(.975) * (standard_dev /sqrt(15))
left_interval = sample_mean - error
right_interval = sample_mean + error

print(paste("The 95% interval is between ", left_interval, " and ", right_interval))


```

## In Class Example 3: Circuit Boards

A random sample of 200 printed circuit boards contains 18 defective or nonconforming units. 
Test the hypothesis that the true fraction nonconforming in the process is 0.10. Use a = 0.05. 

```{r}
#given variables
errors = 18
sample_size = 200
null_hypothesis =0.1
alpha = 0.05

#Equation
Z = ((errors - 0.5) - sample_size * null_hypothesis) / sqrt(sample_size * null_hypothesis * (1 - null_hypothesis))

if(Z > qnorm(1-(alpha/2))) {
  print("REJECT")
}
if(Z < qnorm(1-(alpha/2))) {
  print("ACCEPT")
}

```

## In Class Example 4: Circuit Boards Confidence Intervals

Using the data from the previous example, find a 95% confidence interval for the circuit board defective rate. How would this change if we wanted a 99% confidence interval?

```{r}
total_samples = 200
rejected_applications = 18
alpha = 0.05
fraction_rejected = rejected_applications / total_samples
Z_score = qnorm(1-(alpha/2)) #z is 1.96 for a 95% confidence interval

#Lower Bound
lower_bound = fraction_rejected - Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

#Upper Bound
upper_bound = fraction_rejected + Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

print(paste(round(lower_bound,4), "< p <", round(upper_bound, 4)))

```

```{r}
total_samples = 200
rejected_applications = 18
alpha = 0.01
fraction_rejected = rejected_applications / total_samples
Z_score = qnorm(1-(alpha/2)) #z is 1.96 for a 95% confidence interval

#Lower Bound
lower_bound = fraction_rejected - Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

#Upper Bound
upper_bound = fraction_rejected + Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

print(paste(round(lower_bound,4), "< p <", round(upper_bound, 4)))
```


##In Class Example 5: Output Voltage

The output voltage of a power supply is assumed to be normally distributed. Sixteen observations taken at random on voltage are as follows: 10.35, 9.30, 10.00, 9.96, 11.65, 12.00, 11.25, 9.58, 11.54, 9.95, 10.28, 8.37, 10.44, 9.25, 9.38, and 10.85. 
Create a 95% confidence interval for the standard deviation.
  
```{r}
voltage_data = c(10.35, 9.30, 10.00, 9.96, 11.65, 12.00, 11.25, 9.58, 11.54, 9.95, 10.28, 8.37, 10.44, 9.25, 9.38, 10.85)

s_sqrd = (sd(voltage_data)^2)
degree_freedom = length(voltage_data) - 1

#lower bound
lower_bound = degree_freedom*s_sqrd / qchisq(.975,degree_freedom)

#upper bound
upper_bound = degree_freedom*s_sqrd / qchisq(.025,degree_freedom)

paste("The interval is from ", round(sqrt(lower_bound),3), " to ", round(sqrt(upper_bound),3))


```

There were some back of the book examples that were put on the board, here are their solutions as well

## Back of the Book Solution 4.7
  
Ferric chloride is used as a flux in some types of extraction metallurgy processes. This material is shipped in containers, and the container weight varies. It is important to obtain an accurate estimate of mean container weight. Suppose that from long experience a reliable value for the standard deviation of flux container weight is determined to be 4 lb.  
How large a sample would be required to construct a 95% two-sided confidence interval on the mean that has a total width of 1 lb?

```{r}
#we need the z score, the standard deviation, and the two sided MOE for the sample size equation
#input data
z = qnorm(.975)
stand_dev = 4
margin_of_error = .5

#finish 
sample_size = ((z * stand_dev) / margin_of_error) ^ 2
print(sample_size)
```
  
## Back of the Book Solution 4.8
The diameters of aluminum alloy rods produced on an extrusion machine are known to have a standard
deviation of 0.0001 in. A random sample of 25 rods has an average diameter of 0.5046 in. 
(a) Test the hypothesis that mean rod diameter is 0.5025 in. Assume a two-sided alternative and use a = .05  
(b) Find the P-value for this test.  
(c) Construct a 95% two-sided confidence interval  
  
```{r}
#a
null_hypothesis = .5025
sample_mean = .5046
standard_dev = 0.002

z = ((sample_mean - null_hypothesis)/(standard_dev/sqrt(25)))


Range_z <- qnorm(c(.025, .975))
if(Range_z[1] < z & z < Range_z[2]){
  print("Accept")
} else{
  print("Reject")
}
```
  
```{r}
#b
#calculate the p value from the normal distribution

2*pnorm(-abs(z))
```
  
```{r}
#c
sample_mean = .5046
error = qnorm(.975) * (standard_dev /sqrt(25))
left_interval = sample_mean - error
right_interval = sample_mean + error

print(paste("The 95% interval is between ", left_interval, " and ", right_interval))

```
  
  
  

## Back of the Book Solution 4.10
Two machines are used for filling glass bottles with a soft-drink beverage. The filling processes have known standard deviations liter and liter, respectively. A random sample of bottles from machine 1 and bottles from machine 2 results in average net contents of liters and liters.  

(a) Test the hypothesis that both machines fill to the same net contents, using a = .05. What are your conclusions?   
(b) Find the P-value for this test.  
(c) Construct a 95% confidence interval on the difference in mean fill volume  
```{r}
#a
#enter the data
x1 = 2.04
x2 = 2.07
sd1 = .010
sd2 = .015
n1 = 25
n2 = 20

#test hypothesis

z = (x2 - x1)/sqrt(((sd1^2)/n1)+((sd2^2)/n2)) #equation 4.48

if(z > 1.645){
  print("Reject Null Hypothesis")
}
if(z < 1.645){
  print("Accept Null Hypothesis")
}

```
  
```{r}
#b
#p value
2*pnorm(-abs(z))
```
  
```{r}
#c
error = qnorm(.975) * sqrt(((sd1^2)/n1)+((sd2^2)/n2))

#Left bound
left = x2 - x1 - error

#Right bound
right = x2 - x1 + error

print(paste("The 95% interval is", round(left,5), "< difference in true means <", round(right,5)))
```
  

## Back of the Book Solution 4.15
A random sample of 500 connecting rod pins contains 65 nonconforming units. Estimate the process fraction nonconforming.  
(a) Test the hypothesis that the true fraction defective in this process is 0.08. Use a = .05  
(b) Find the P-value for this test.  
(c) Construct a 95% upper confidence interval on the true process fraction nonconforming.  

```{r}
#a
sample_size = 500
nonconfirming = 65

#given variables
errors = 65
sample_size = 500
null_hypothesis = 0.08
alpha = 0.05

#Equation
Z = ((errors - 0.5) - sample_size * null_hypothesis) / sqrt(sample_size * null_hypothesis * (1 - null_hypothesis))

if(Z > qnorm(1-(alpha/2))) {
  print("REJECT")
}
if(Z < qnorm(1-(alpha/2))) {
  print("ACCEPT")
}



```

```{r}
#b
#p value
2*pnorm(-abs(Z))
```

```{r}
#c
alpha = 0.05
fraction_rejected = errors / sample_size
Z_score = qnorm(1-(alpha)) 

#Upper Bound
upper_bound = fraction_rejected + Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / sample_size)

print(paste("The 95% upper bound is", round(upper_bound, 3)))

```
  



