---
title: "Chapter 4 Part 2: Example Walkthroughs"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


## Example 4.7: Finding the Power of a Test

The mean contents of coffee cans filled on a particular production line are being studied. Standards specify that the mean contents must be 16.0 oz, and from past experience it is known that the standard deviation of the can contents is 0.1 oz. The hypotheses are h0 = 16.1 and h1 = 16.0.  
A random sample of nine cans is to be used, and the type I error probability is specified as a = .05. h0 is rejected if Z > 1.96.   
Find the probability of type II error and the power of the test, if the true mean contents are equal to 16.1.  

  
```{r}
#Given Variables
h0 = 16.1
h1 = 16.0
sigma = .1
n = 9

#Create Z test function
#we can create functions in R that pre-define the inputs and the outputs
powerZtest = function(alpha = 0.05, sigma, n, delta){ #here we define what the user will need to input to use our function
  zcr = qnorm(p = 1-alpha, mean = 0, sd = 1) #here is the code that finds the power of a Z test
  s = sigma/sqrt(n)
  power = 1 - pnorm(q = zcr, mean = (delta/s), sd = 1)
  return(power) #and this is what the function returns
}
#functions will make our code much faster in the future

#now that we've created the function, let's use it!
powerZtest(n = n, sigma = sigma, delta = (h0-h1))


```
  
  
## Example 4.8: Comparing Paint Formulations

A product developer is interested in reducing the drying time of a primer paint. Two formulations of the paint are tested; formulation 1 is the standard chemistry, and formulation 2 has a new drying ingredient that should reduce the drying time. From experience, it is known that the standard deviation of drying time is eight minutes, and this inherent variability should be unaffected by the addition of the new ingredient.  
Ten specimens are painted with formulation 1, and another 10 specimens are painted with formulation 2; the 20 specimens are painted in random order. The two sample average drying times are min and min, respectively. 
  
What conclusions can the product developer draw about the effectiveness of the new ingredient, using a = 0.05?




```{r}
#Given variables
x_1 = 121
x_2 = 112
sample_1 = 10
sample_2 = 10
sd = 8

#The Null Hypothesis is that the mean drying time for paints is the same

#Z Score calculation
Z = (x_1 - x_2) / sqrt( ( (sd^2) / sample_1 ) + ( ( sd^2) / sample_2 ) )

if(Z > 1.645){
  print("Reject Null Hypothesis")
}
if(Z < 1.645){
  print("Accept Null Hypothesis")
}

```

  
  
## Example 4.12: The Paper Tensile Strength Experiment

Consider the paper tensile strength experiment described in Section 4.5.1. Use the analysis of variance to test the hypothesis that different hardwood concentrations do not affect the mean tensile strength of the paper. 

```{r}

#R has functions for calculating anova, but the example specifies that we should use the sum of squares method. If you're interested, check out the aov() function for more functionality. 

#Load dataset
Tensile_observations = data.frame(Hardwood_concentration = c(5,10,15,20), One = c(7,12,14,19), Two = c(8,17,18,25), Three = c(15,13,19,22), Four = c(11,18,17,23), Five = c(9,19,16,18), Six = c(10,15,18,20))

#grab the sum using the rowSums function, which sums the rows from each specified column
Tensile_observations$Totals = rowSums(Tensile_observations[,c("One", "Two", "Three", "Four", "Five", "Six")])
#the average is the total divided by 6
Tensile_observations$Averages = Tensile_observations$Totals / 6

#calculate the sum of squares
Sum_Squares_Total = sum(sum(Tensile_observations$One ^ 2), sum(Tensile_observations$Two ^ 2), sum(Tensile_observations$Three ^ 2), sum(Tensile_observations$Four ^ 2),sum(Tensile_observations$Five ^ 2), sum(Tensile_observations$Six ^ 2)) - (sum(Tensile_observations$Totals) ^ 2) / 24

Sum_Squares_Treatment = (sum(Tensile_observations$Totals ^ 2) / 6) - (sum(Tensile_observations$Totals) ^ 2) / 24

Sum_Squares_E = Sum_Squares_Total - Sum_Squares_Treatment

#factor is a data type that allows us to categorize the data, making this process easier
Tensile_observations$Hardwood_concentration = as.factor(Tensile_observations$Hardwood_concentration)

#a is the number of observations
#n is the number of columns
a = 4
n = 6
error_mean_square = Sum_Squares_E / (a * (n-1))

#find the F statistic
F_stat = (Sum_Squares_Treatment / (a-1) ) / (Sum_Squares_E / (a * ( n -1)))

#compare the F statistic to the target
if(F_stat > qf(c(.01, .99), 3, 20)[2]){
  print("Reject Null Hypothesis")
} else {
  print("Do not Reject Null Hypothesis")
}

```



## Example 4.13: Fitting a Linear Regression Model

Sixteen observations on the operating cost of a branch office of a finance company (y) and two predictor variables—number of new loan applications and number of loans outstanding. Fit a multiple linear regression model to these data.
  
Here's model fitting in R

```{r}
#Get the data
Finance_data = data.frame(Observation = c(1:16), Applications = c(80, 93, 100, 82, 90, 99, 81, 96, 94, 93, 97, 95, 100, 85, 86, 87), Outstanding = c(8,9,10,12,11,8,8,10,12,11,13,11,8,12,9,12), Cost = c(2256,2340,2426,2293,2330,2368,2250,2409,2364,2379,2440,2364,2404,2317,2309,2328))

#Fit the model
#the second parameter can be read "predict cost using the columns outstanding and applications"
Finance_model = lm(data = Finance_data, Cost ~ Outstanding + Applications)
summary(Finance_model)

```
  
  

## Example 4.15: A Confidence Interval on a Regression Coefficient

Construct a 95% confidence interval for the parameter in Example 4.13.


```{r}
Finance_data = data.frame(Observation = c(1:16), Applications = c(80, 93, 100, 82, 90, 99, 81, 96, 94, 93, 97, 95, 100, 85, 86, 87), Outstanding = c(8,9,10,12,11,8,8,10,12,11,13,11,8,12,9,12), Cost = c(2256,2340,2426,2293,2330,2368,2250,2409,2364,2379,2440,2364,2404,2317,2309,2328))

#re create the model from 4.13 
Finance_model = lm(data = Finance_data, Cost ~ Outstanding + Applications)

#the default confint is 95%
confint(Finance_model, "Applications")


```

