---
title: "Chapter 4 Part 1: Solutions"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


```{r include=FALSE}
library(knitr)
```

## In Class Example 1: Aircraft Bearings

The inside diameters of bearings used in an aircraft landing gear assembly are known to have a standard deviation of .002. A random sample of 15 bearings has an average inside diameter of 8.2535 cm.  
Test the hypothesis that the mean inside bearing diameter is 8.25cm. Use a two-sided alternative and a = .05.  


```{r}
null_hypothesis = 8.25
sample_mean = 8.2535
standard_dev = 0.002

t_stat = (sample_mean - null_hypothesis) / (standard_dev / sqrt(15))

Range_t <- qt(c(.025, .975), df = 14)
if(Range_t[1] < t_stat & t_stat < Range_t[2]){
  print("Accept")
} else{
  print("Reject")
}


```

## In Class Example 2: Aircraft Bearings Confidence intervals

Construct a 95% two sided confidence interval on the mean bearing diameter using data from the previous question.

```{r}
sample_mean = 8.2535
error = qt(.975, df = 14) * (standard_dev /sqrt(15))
left_interval = sample_mean - error
right_interval = sample_mean + error

print(paste("The 95% interval is between ", left_interval, " and ", right_interval))


```

## In Class Example 3: Circuit Boards

A random sample of 200 printed circuit boards contains 18 defective or nonconforming units. 
Test the hypothesis that the true fraction nonconforming in the process is 0.10. Use a = 0.05. 

```{r}
#given variables
errors = 18
sample_size = 200
null_hypothesis =0.1
alpha = 0.05

#Equation
Z = ((errors - 0.5) - sample_size * null_hypothesis) / sqrt(sample_size * null_hypothesis * (1 - null_hypothesis))

if(Z > qnorm(1-(alpha/2))) {
  print("REJECT")
}
if(Z < qnorm(1-(alpha/2))) {
  print("ACCEPT")
}

```

## In Class Example 4: Circuit Boards Confidence Intervals

Using the data from the previous example, find a 95% confidence interval for the circuit board defective rate. How would this change if we wanted a 99% confidence interval?

```{r}
total_samples = 200
rejected_applications = 18
alpha = 0.05
fraction_rejected = rejected_applications / total_samples
Z_score = qnorm(1-(alpha/2)) #z is 1.96 for a 95% confidence interval

#Lower Bound
lower_bound = fraction_rejected - Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

#Upper Bound
upper_bound = fraction_rejected + Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

print(paste(round(lower_bound,4), "< p <", round(upper_bound, 4)))

```

```{r}
total_samples = 200
rejected_applications = 18
alpha = 0.01
fraction_rejected = rejected_applications / total_samples
Z_score = qnorm(1-(alpha/2)) #z is 1.96 for a 95% confidence interval

#Lower Bound
lower_bound = fraction_rejected - Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

#Upper Bound
upper_bound = fraction_rejected + Z_score * sqrt((fraction_rejected * (1 - fraction_rejected)) / total_samples)

print(paste(round(lower_bound,4), "< p <", round(upper_bound, 4)))
```


##In Class Example 5: Output Voltage

The output voltage of a power supply is assumed to be normally distributed. Sixteen observations taken at random on voltage are as follows: 10.35, 9.30, 10.00, 9.96, 11.65, 12.00, 11.25, 9.58, 11.54, 9.95, 10.28, 8.37, 10.44, 9.25, 9.38, and 10.85. 
Create a 95% confidence interval for the standard deviation.
  
```{r}
voltage_data = c(10.35, 9.30, 10.00, 9.96, 11.65, 12.00, 11.25, 9.58, 11.54, 9.95, 10.28, 8.37, 10.44, 9.25, 9.38, 10.85)

s_sqrd = (sd(voltage_data)^2)
degree_freedom = length(voltage_data) - 1

#lower bound
lower_bound = degree_freedom*s_sqrd / qchisq(.975,degree_freedom)

#upper bound
upper_bound = degree_freedom*s_sqrd / qchisq(.025,degree_freedom)

paste("The interval is from ", round(sqrt(lower_bound),3), " to ", round(sqrt(upper_bound),3))


```



