---
title: "Everything about R"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

## R Tutorial For The Lost
  
This tutorial will cover every function and concept that we learned about R in this course, and could prove to be a useful study guide for exam 2. 
  
### Create a Variable

```{r eval = F}
#two ways
my_variable = 5
my_variable <- 5
```

### Create a Vector (sequence of data elements)

```{r eval = F}
#c stands for concatenate
my_vector = c(1,2,3)
```

### Create a Dataframe (a table of data with rows and columns, analogous to a spreadsheet)

```{r eval = F}
my_dataframe = data.frame(first_column = c(1,2,3), second_column = c(4,5,6))

```

### Stem and Leaf Plot
```{r eval = F}
stem(data)
```
### Histogram
```{r eval = F}
hist(data, breaks = number_of_bins, xlab = "My X Label", ylab = "My Y Label", main = "Graph Title")
```

### BoxPlot
```{r eval = F}
boxplot(data, ylim = my_y_limits)
```

### Normal Distributions
```{r eval = F}
#Density
dnorm(x, mean = 0, sd = 1)

#Direct Look-Up
pnorm(q, mean = 0, sd = 1, lower.tail = TRUE)

#Inverse Look-Up
qnorm(p, mean = 0, sd = 1, lower.tail = TRUE)

#Random Number Generation
rnorm(n, mean = 0, sd = 1)

#lower.tail = FALSE gives the compliment
```

### Binomial Distributions
```{r eval = F}
#same as normal, but replacing norm with binom
#Direct Look-Up
pbinom(number, mean, sd)

#Inverse Look-Up
qnorm(percentile, mean, sd)

#Density/P.D.F.
dnorm(number, mean, sd)
```
  
### Formatting

```{r eval = F}
#print characters and strings
print(paste(my_number, "my string"))

#round
round(my_number, number_digits)
```

### Probability Plots

```{r eval = F}
library(e1071)
probplot(my_data, qdist = qnorm)
```

