---
title: 'Chapter 8 End of Chapter Solution'
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


```{r include=FALSE}
library(knitr)
```

Currently, the questions come from the 6th edition of the QC book. Different version have the same problems but different problem numbers.  

## Problem 8.5: Capability Calculation

A process is in control with x_bar = 100, s = 1.05, and n = 5. The process specifications are at 95 ± 10. The quality characteristic has a normal distribution.  
(a) Estimate the potential capability.  
(b) Estimate the actual capability.  
(c) How much could the fallout in the process be reduced if the process were corrected to operate at the nominal specification? 

```{r}
#potential capability

#we estimate sigma using c_4 and s
c_4 = .94
s = 1.05
sigma = (s /c_4 )

#find Cp, which is potential capability
Cp <- (105 - 85) / (6 * sigma)


#Cpk is actual capability
upper = (105 - 100) / (3 * sigma)
lower = (100 - 85) / (3 * sigma)

Cpk = min(upper, lower)



```

  
## Problem 8.9: Processing Data
  
  
Consider the two processes shown in Table 8E.1 (the
sample size n = 5). Specifications are at 100 ± 10. Calculate Cp, Cpk, and Cpm and interpret these ratios.  
```{r}
x_a_mean = 100
s_a = 3
x_b_mean = 105
s_b = 1

#process a
Cp_a = (110 - 90) / (6 * s_a)
Cpk_upper_a = (110 - x_a_mean) / (3 * s_a)
Cpk_lower_a = (x_a_mean - 90) / (3 * s_a)
min(Cpk_upper_a, Cpk_lower_a )

#process b
Cp_b = (110 - 90) / (6 * 1)

Cpk_upper_b = (110 - x_b_mean) / (3 * s_b)
Cpk_lower_b = (x_b_mean - 90) / (3 * s_b)
min(Cpk_upper_b, Cpk_lower_b )

#Cpm
#ξ = xi
xi_b = (x_b_mean - (.5*(110 + 90))) / s_b


Cpm_b = Cp_b / sqrt(1 + xi_b^2)
Cpm_b


```


  
## Problem 8.11: Chemical Ingredient Container Weight
  
The weights of nominal 1-kg containers of a concentrated chemical ingredient are shown in Table 8E.2. Prepare a normal probability plot of the data and estimate process capability.

```{r}
#read in the data
weights <- c(0.9475, 0.9775, 0.9965, 1.0075, 1.0180, 0.9705, 0.9860, 0.9975, 1.0100, 1.0200, 0.9770, 0.9960, 1.0050, 1.0175, 1.0250)

library(e1071)
probplot(weights)
```

```{r}
#see section 8.2.2 for explained methodology
#84th percentile
#sigma can be estimated by the 84th percentile minus the 50th percentile
#from the chart, we see that the 84th percentile is around 1.021
#the 50th percentile is around .995
sigma = 1.021 - 1

#6 sigma is sufficient to estimate
sigma * 6
```

  
  
## Problem 8.15: Electric Utilities

An electric utility tracks the response time to customerreported outages. The data in Table 8E.5 are a random sample of 40 of the response times (in minutes) for one operating division of this utility during a single month.  
  
(a) Estimate the capability of the utility’s process for responding to customer-reported outages.  
(b) The utility wants to achieve a 90% response rate in under two hours, as response to emergency outages is an important measure of customer satisfaction. What is the capability of the process with respect to this objective?  

```{r}

```

  
## Problem 8.19: Company Capability Confidence

  
  
A company has been asked by an important customer to demonstrate that its process capability ratio Cp exceeds 1.33. It has taken a sample of 50 parts and obtained the point estimate . Assume that the quality characteristic follows a normal distribution. Can the company demonstrate that Cp exceeds 1.33 at the 95% level of confidence? What level of confidence would give a one-sided lower confidence limit on Cp that exceeds 1.33?  
  
  
## Problem 8.25: Operator Variability
  
  
Ten parts are measured three times by the same operator in a gauge capability study. The data are shown in Table 8E.7.  
(a) Describe the measurement error that results from the use of this gauge.  
(b) Estimate total variability and product variability.  
(c) What percentage of total variability is due to the gauge?  
(d) If specifications on the part are at 100 ± 15, find the P/T ratio for this gauge. Comment on the adequacy of the gauge.  

  
## Problem 8.27: Gauge Capability
  
  
The data in Table 8E.9 were taken by one operator during a gauge capability study.  
(a) Estimate gauge capability.  
(b) Does the control chart analysis of these data indicate any potential problem in using the gauge?  
  

  


