---
title: 'Chapter 8: Example Walkthrough'
author: Tyler Richards
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


```{r include=FALSE}
library(knitr)
library(here)
```

## Example 8.1: Estimating Process Capability with a Histogram

Figure 8.2 presents a histogram of the bursting strength of 100 glass containers. The data are shown in Table 8.1. What is the capability of the process?
  
  
```{r}
Glass_containers <- read.csv("Glass_containers.csv")

#analysis
Glass_avg <- mean(Glass_containers$x)
Glass_std <- sd(Glass_containers$x)

print(paste("99.73 percent of all the glass containers will burst between ", Glass_avg - 3*Glass_std, " and ", Glass_avg + 3*Glass_std, "."))

#histogram
hist(Glass_containers[,c(1)])
```
  
  
  
## Example 8.2: One-Sided Process-Capability Ratios

Construct a one-sided process-capability ratio for the container bursting-strength data in Example 8.1. Suppose that the lower specification limit on bursting strength is 200 psi.  

  
  
  
```{r}
#read in data
Glass_containers <- read.csv("Glass_containers.csv")

#set variables
Glass_avg <- mean(Glass_containers$x)
Glass_std <- sd(Glass_containers$x)
LSL_bursting_strength <- 200


#Use equation 8.8 
Lower_capability_ratio <- (Glass_avg - LSL_bursting_strength) / (3 * Glass_std)

print(Lower_capability_ratio)
```


## Example 8.4: Confidence Interval in Cp

Suppose that a stable process has upper and lower specifications at USL = 62 and LSL = 38. A sample of size n = 20 from this process reveals that the process mean is centered approximately at the midpoint of the specification interval and that the
sample standard deviation s = 1.75. Find a 95% confidence
interval on C.  
  
  
  

```{r}
#enter data
USL <- 62
LSL <- 38
n = 20
s = 1.75

#Find point estimate
C = (USL - LSL) / (6 * s)

#Lower Bound from equation 8.20
Lower_b <- C * sqrt(qchisq(.025, n - 1)/(n - 1))

#Upper Bound from equation 8.20
Upper_b <- C * sqrt(qchisq(.975, n - 1)/(n - 1))

#confidence interval

print(paste("The CI is inbetween", round(Lower_b,3), "and", round(Upper_b,3)))




```

## Example 8.5: A Confidence Interval in Cpk
  
A sample of size n = 20 from a stable process is used to estimate Cpk, with the result that Cpk = 1.33. Find an approximate 95% confidence interval on Cpk.  
  
  
  
```{r}
#assign variables
Cpk <- 1.33
z <- qnorm(.975)
n = 20

#Lower bound using equation 8.21
Lower_b <- Cpk * (1 - z * sqrt((1 / (9 * n * (Cpk ^ 2))) + (1 / (2 * (n-1)))))

#Upper
Upper_b <- Cpk * (1 + z * sqrt((1 / (9 * n * (Cpk ^ 2))) + (1 / (2 * (n-1)))))

#Now put it all together
print(paste("The CI is inbetween", round(Lower_b,2), "and", round(Upper_b,2)))

```
  
  
  
## Example 8.7.2: The Analysis of Variance Method
  
  
Use Table 8.8 to show the analysis of variance for the experiment measuring thermal inpedance versus part number, operator/inspector.  


```{r}
#read in the data
Thermal_Impedance <- read.csv("Thermal_Impedance.csv")

#Part number should be a categorical variable, not a discrete numeric one
#The factor data type is a way to reshape the data to make the column categorical

Thermal_Impedance$Part_Num <- as.factor(Thermal_Impedance$Part_Num)

#create a linear model to perform anova on
#the example specifies the formula
#multiplication in a formula finds the interaction term
Thermal_fit <- lm(Value ~ Part_Num + Inspector + Part_Num * Inspector, data = Thermal_Impedance)

#perform and print the anova
anova(Thermal_fit)
```



