---
title: 'Chapter 6 Exercise Solutions'
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


```{r include=FALSE}
library(knitr)
```


## Book Problem 6.5: Soft Drinks

The fill volume of soft-drink beverage bottles is an important quality characteristic. The volume is measured (approximately) by placing a gauge over the crown and comparing the height of the liquid in the neck of the bottle against a coded scale. On this scale, a reading of zero corresponds to the correct fill height. Fifteen samples of size n = 10 have been analyzed, and the fill heights are shown in Table 6E.5.  
  
  
a. Set up x and s control charts on this process.
Does the process exhibit statistical control?  
b. Set up an R chart, and compare with the s chart
in part (a)  
c. Remove the last observations in each of the last 5 samples and set up x and s control charts on this process

```{r include = F}
library(here)
setwd(here("Chapter_6"))
```

```{r message=F}
#a
library(qcc)
#see the Manual Data Entry Tutorial for instructions on getting the data to a csv format
Fill_height <- read.csv("Fill_height.csv") #read.csv reads a csv file into R
Fill_height <- as.data.frame(t(Fill_height)) #the data needs to be flipped using the t() function, which transposes matrices and dataframes. We then turn that transpose into a dataframe with the as.data.frame function

qcc(data = Fill_height, type = "xbar")
qcc(data = Fill_height, type = "S")
```
  
```{r}
#b
#create an R chart using the qcc function
qcc(data = Fill_height, type = "R")
```

```{r}
#c
#removing the last 5 rows in the 15th column by setting them to NA
Fill_height[6:10, 15] <- NA
qcc(data = Fill_height, type = "xbar")
qcc(data = Fill_height, type = "S")
```

## Book Problem 6.9: Piston Ring  

  
Consider the piston ring data shown in Table 6.3.
Set up x and R control charts on this process. Is the process in statistical control?
  
```{r}
#enter data into R
Piston_data = data.frame(Observation1 = c(74.03, 73.995, 73.988, 74.002, 73.992,	74.009,	73.995,	73.985,	74.008,	73.998,	73.994,	74.004,	73.983,	74.006,	74.012,	74,	73.994,	74.006,	73.984,	74,	73.982,	74.004,	74.01,	74.015,	73.982), Observation2 = c(74.002,	73.992,	74.024,	73.996,	74.007,	73.994,	74.006,	74.003,	73.995,	74,	73.998,	74,	74.002,	73.967,	74.014,	73.984,	74.012,	74.01,	74.002,	74.01,	74.001,	73.999,	73.989,	74.008,	73.984), Observation3 = c(74.019,	74.001,	74.021,	73.993,	74.015,	73.997,	73.994,	73.993,	74.009,	73.99,	73.994,	74.007,	73.998,	73.994,	73.998,	74.005,	73.986,	74.018,	74.003,	74.013,	74.015,	73.99,	73.99,	73.993,	73.995), Observation4 = c(73.992,	74.011,	74.005,	74.015,	73.989,	73.985,	74,	74.015,	74.005,	74.007,	73.995,	74,	73.997,	74,	73.999,	73.998,	74.005,	74.003,	74.005,	74.02,	74.005,	74.006,	74.009,	74,	74.017), Observation5 = c(74.008,	74.004,	74.002,	74.009,	74.014,	73.993,	74.005,	73.988,	74.004,	73.995,	73.99,	73.996,	74.012,	73.984,	74.007,	73.996,	74.007,	74,	73.997,	74.009,	73.996,	74.009,	74.014,	74.01,	74.013))

#create graphs using the qcc function
qcc(data = Piston_data, type = "xbar")
qcc(data = Piston_data, type = "R")
```

  
## Book Problem 6.10: Piston Ring Cont
  
Table 6E.7 shows 15 additional samples for the piston ring process (Table 6.3), taken after the initial control charts were established. Plot these data on the x and R chart developed in Exercise 6.9. Is the process in control?  

```{r}
#read in new data (again, see the tutorial for how to get data from the textbook into R)
New_Piston_data <- read.csv("Piston_data_new.csv")
colnames(New_Piston_data) <- colnames(Piston_data) #make the column names match each other
Combined_Pison <- rbind(Piston_data, New_Piston_data) #rbind combines the rows of the two dataframes using the column names

qcc(data = Combined_Pison, type = "xbar")
qcc(data = Combined_Pison, type = "R")
```
  
  
  
  
  
## Book Problem 6.56: Polymer Viscosity

Continuation of Exercise 6.55. The next five measurements on viscosity are 3163, 3199, 3054, 3147, and 3156. Do these measurements indicate that the process is in statistical control?  
  
  

```{r}
#read data into R
Viscosity_data <- read.csv("Polymer_Viscosity_data.csv")

#set column names
names(Viscosity_data) <- c("Sample", "Value")

#create a dataframe of the new data
new_Viscosity <- data.frame(Sample = 21:25, Value = c(3163, 3199, 3054, 3147, 3156))

#combine the two
total_Viscosity <- rbind(new_Viscosity, Viscosity_data)

#graph!
qcc(data = new_Viscosity$Value, type = "xbar.one")

```

