---
title: "Chapter 6: Example Walkthroughs"
author: Tyler Richards
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

## Example 6.1: X and R Charts for a Manufacturing Process
  
A hard-bake process (see Section 5.3.1) is used in conjunction with photolithography in semiconductor manufacturing. We wish to establish statistical control of the flow width of the resist in this process using and R charts. Twenty-five samples, each of size five wafers, have been taken when we think the process is in control. The interval of time between samples or subgroups is one hour. The flow width measurement data (in x microns) from these samples are shown in Table 6.1.  
  
  

```{r eval = F, message=F}
#there is a package in R called qcc, which stands for quality control charts. Perfect!
#qcc "provides quality control tools for statistical process control" 
#it takes observations from different samples of a process and outputs the desired control charts.
#qcc is used heavily in industry and research, and is generally versatile, two great reasons for learning the package

install.packages("qcc")
```

```{r message=F}
#load the package
library(qcc)

#input the data from the textbook
flow_Width = data.frame(Wafer1 = c(1.3235,	1.4314,	1.4284,	1.5028,	1.5604,	1.5955,	1.6274,	1.4190,	1.3884,	1.4039,	1.4158,	1.5821,	1.2856,	1.4951,	1.3589,	1.5747,	1.3680,	1.4163,	1.5796,	1.7106,	1.4371,	1.4738,	1.5917,	1.6399,	1.5797), Wafer2 = c(1.4128,	1.3592,	1.4871,	1.6352,	1.2735,	1.5451,	1.5064,	1.4303,	1.7277,	1.6697,	1.7667,	1.3355,	1.4106,	1.4036,	1.2863,	1.5301,	1.7269,	1.3864,	1.4185,	1.4412,	1.5051,	1.5936,	1.4333,	1.5243,	1.3663 ), Wafer3 = c(1.6744,	1.6075,	1.4932,	1.3841,	1.5265,	1.3574,	1.8366,	1.6637,	1.5355,	1.5089,	1.4278,	1.5777,	1.4447,	1.5893,	1.5996,	1.5171,	1.3957,	1.3057,	1.6541,	1.2361,	1.3485,	1.6583,	1.5551,	1.5705,	1.6240), Wafer4 = c(1.4573,	1.4666,	1.4324,	1.2831,	1.4363,	1.3281,	1.4177,	1.6067,	1.5176,	1.4627,	1.5928,	1.3908,	1.6398,	1.6458,	1.2497,	1.1839,	1.5014,	1.6210,	1.5116,	1.3820,	1.5670,	1.4973,	1.5295,	1.5563,	1.3732), Wafer5 = c(1.6914,	1.6109,	1.5674,	1.5507,	1.6441,	1.4198,	1.5144,	1.5519,	1.3688,	1.5220,	1.4181,	1.7559,	1.1928,	1.4969,	1.5471,	1.8662,	1.4449,	1.5573,	1.7247,	1.7601,	1.4880,	1.4720,	1.6866,	1.5530,	1.6887))

#the qcc function takes a few parameters (also called inputs)
#the first parameter is the dataframe, and the second is the type of graph
#we want an xbar graph, so we specify that in the parameter called type
#to find all the parameters of a function and their descriptions, type ? before the function name
#in this case, run the line below for qcc information
# ?qcc

#calling the qcc function stores descriptive statistics in your variable name, as well as shows the graph by default

xbar_flow_data_graph = qcc(data = flow_Width, type = "xbar")

```

```{r}
#for the R chart, just change the parameter
R_flow_data_graph = qcc(flow_Width, type = "R")

```
  

```{r}
#for more info about the graph, use the summary function
#we've used the summary function before, often for linear models. It's a great function for understanding your data and ouput 
summary(R_flow_data_graph)
```
  
  

## Example 6.3: X and s Charts for the Piston Ring Data
  
Construct and interpret x and s charts using the piston ring inside diameter measurements in Table 6.3.  
  
  

```{r}
#input the data
#the good news is that the large majority of the time in the real world, your data will come in a .txt or .csv format, and you will not have to manually input it
Piston_data = data.frame(Observation1 = c(74.03, 73.995, 73.988, 74.002, 73.992,	74.009,	73.995,	73.985,	74.008,	73.998,	73.994,	74.004,	73.983,	74.006,	74.012,	74,	73.994,	74.006,	73.984,	74,	73.982,	74.004,	74.01,	74.015,	73.982), Observation2 = c(74.002,	73.992,	74.024,	73.996,	74.007,	73.994,	74.006,	74.003,	73.995,	74,	73.998,	74,	74.002,	73.967,	74.014,	73.984,	74.012,	74.01,	74.002,	74.01,	74.001,	73.999,	73.989,	74.008,	73.984), Observation3 = c(74.019,	74.001,	74.021,	73.993,	74.015,	73.997,	73.994,	73.993,	74.009,	73.99,	73.994,	74.007,	73.998,	73.994,	73.998,	74.005,	73.986,	74.018,	74.003,	74.013,	74.015,	73.99,	73.99,	73.993,	73.995), Observation4 = c(73.992,	74.011,	74.005,	74.015,	73.989,	73.985,	74,	74.015,	74.005,	74.007,	73.995,	74,	73.997,	74,	73.999,	73.998,	74.005,	74.003,	74.005,	74.02,	74.005,	74.006,	74.009,	74,	74.017), Observation5 = c(74.008,	74.004,	74.002,	74.009,	74.014,	73.993,	74.005,	73.988,	74.004,	73.995,	73.99,	73.996,	74.012,	73.984,	74.007,	73.996,	74.007,	74,	73.997,	74.009,	73.996,	74.009,	74.014,	74.01,	74.013))

#for the S chart, just switch the type parameter in the qcc function
s_piston_data_chart = qcc(Piston_data, type = "S")
```

```{r}
x_piston_data_chart = qcc(Piston_data, type = "xbar")

```
  
```{r}
#let's get some more info about these charts
summary(x_piston_data_chart)

summary(s_piston_data_chart)
```
  
  
## Example 6.4: X and s Charts for the Piston Ring Data, Variable Sample Size
  
Consider the data in Table 6.4, which is a modificaiton of the piston-ring data used in Example 6.3. Note that the sample sizes vary from n = 3 to n = 5. Use the procedure described on page 255 to set up the x and s control charts.
  
  
```{r}
#input the new data
Piston_data_2 = data.frame(Observation1 = c(74.03,	73.995,	73.988,	74.002,	73.992,	74.009,	73.995,	73.985,	74.008,	73.998,	73.994,	74.004,	73.983,	74.006,	74.012,	74,	73.994,	74.006,	73.984,	74,	73.982,	74.004,	74.01,	74.015,	73.982), Observation2 = c(74.002,	73.992,	74.024,	73.996,	74.007,	73.994,	74.006,	74.003,	73.995,	74,	73.998,	74,	74.002,	73.967,	74.014,	73.984,	74.012,	74.01,	74.002,	74.01,	74.001,	73.999,	73.989,	74.008,	73.984), Observation3 = c(74.019,	74.001,	74.021,	73.993,	74.015,	73.997,	73.994,	73.993,	74.009,	73.99,	73.994,	74.007,	73.998,	73.994,	73.998,	74.005,	73.986,	74.018,	74.003,	74.013,	74.015,	73.99,	73.99,	73.993,	73.995), Observation4 = c(73.992,	NA,	74.005,	74.015,	73.989,	73.985,	74,	74.015,	74.005,	74.007,	73.995,	74,	NA,	74,	NA,	73.998,	74.005,	74.003,	74.005,	NA,	74.005,	74.006,	74.009,	74,	74.017), Observation5 = c(74.008,	NA,	74.002,	74.009,	74.014,	NA,	NA,	73.988,	NA,	73.995,	73.99,	73.996,	NA,	73.984,	NA,	73.996,	NA,	74,	73.997,	NA,	73.996,	74.009,	74.014,	74.01,	74.013))
#the only difference between this data and the previous data is that there are NA values in this example
#NA stands for Not Available, and represents missing data
#for many R functions, we will have to explicitly tell R how to deal with NA values (should they be treated as 0s? Omitted from the calculation entirely?)
#the qcc function takes care of all of that for us
s_pison_data_2_chart = qcc(Piston_data_2, type = "S")
```

```{r}
x_piston_data_2_chart = qcc(Piston_data_2, type = "xbar")

```

```{r}
#the variable LCL and UCL values can be found by running 
summary(x_piston_data_2_chart$limits)

```
  
  